### 2021-09-15 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
Some additional edits

The calculated values reported in Table \ref{tab-noncharg} are component power, mass flow fractions, and counter-flow heat exchanger specifications. Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to 400$^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off of a parametric study on the MC mass flow fraction. Values listed in the Cold TES Temperature row are set to values of 390$^{\circ}$C, 410$^{\circ}$C, or 440$^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency. Cycles with data entries labeled not applicable (N/A) do not contain the component listed and therefore do not have values associated with the component.

@@

The two-cycle configuration has the CSP and LFR operating in separate recompression cycles when the focus is on electrical generation, therefore these two cycles are analyzed individually. C-LFR-ON has the highest efficiency during unconstrained operation with a gain of 1.8\%. The unconstrained case allows for smaller temperature gradient across the LFR, an increase in recuperator effectiveness, and an increase in recuperator capacitance ratio, all of which reduce sources of irreversibility in the cycle \cite{klein_nellis_2011}. According to studies carried out by our industry partner, Westinghouse, increasing the LFR sCO$_2$ inlet temperature above the design value of 400$^{\circ}$C has a negative effect on LFR HX outlet temperature, effectively demanding an ideal LFR heat exchanger. Additionally, Westinghouse concluded that a lower sCO$_2$, down to 340$^{\circ}$C, is desirable for LFR heat generation efficiency. The sCO$_2$ inlet temperature to the LFR increases by 15.1$^{\circ}$C to a value of 415.1$^{\circ}$C, reducing LFR heat generation efficiency and demanding a larger, more idealized, LFR heat exchanger.   
\hl{would I need more information on the LFR from westinghouse (ie report) to make these statements? additionally a conclusion to these statements needs more supporting detail, should I go with the higher efficiency or the cycle that I know works with design values?}

C-CSP-ON is not affected by constrained or unconstrained LFR sCO$_2$ inlet temperature during non-charging configuration because the two cycles are not tethered. Two individual studies were conducted on the C-CSP-ON cycle cold TES temperature, one with a lower design value of 390$^{\circ}$C and another with a higher value of 440$^{\circ}$C. A cold TES temperature of 410$^{\circ}$C was excluded since it can be presumed to have an efficiency intermediate between the 390$^{\circ}$C and 440$^{\circ}$C calculated values. Cold TES temperature was found to have a negligible effect on cycle efficiency between the two studied cases, with the 440$^{\circ}$C case gaining 0.35\%. The component that has the largest change in values is the CSP HX with a large drop in capacitance ratio and UA value, therefore the lower temperature of 390$^{\circ}$C for cold TES temperature is ideal increasing the performances of the heat exchanger.

\subsubsection{C-1HTR1T-ON}
The single cycle configuration, C-1HTR1T-ON, has the CSP and LFR heat additions in parallel causing identical inlet conditions. Identical inlet conditions lead to a lower bound of 410$^{\circ}$C on the cold TES temperature when the sCO$_2$ LFR inlet temperature is constrained to 400$^{\circ}$C. A supplementary 440$^{\circ}$C cold TES study is ran to test the effects that higher temperature storage has on cycle efficiency. Raising the temperature of the cold TES from 410$^{\circ}$C to 440$^{\circ}$C had no effect on cycle efficiency but did raise the solar salt mass flow rate to accommodate for the lower temperature difference across the CSP HX hot side. Increasing the solar salt mass flow rate requires more storage for the same heat input and larger pumps increasing the cost of the system. Therefore, a lower cold TES temperature is desirable. Without the constraint on the sCO$_2$ LFR inlet temperature, a study is additionally conducted with cold TES temperature set to 390$^{\circ}$C. Of these three sensitivity studies, the cycle that yielded the highest efficiency is the unconstrained, 390$^{\circ}$C cold TES with an efficiency gain of 0.68\% over the constrained cases. The high temperature difference between the hot and cold TES reduces the mass flow rate of solar salt and subsequent cost of system components. The sCO$_2$ LFR inlet temperature for the 390$^{\circ}$C cold TES study is 380$^{\circ}$C, which increases the performance of the LFR heat exchanger as well as allowing for a higher LFR efficiency.

\subsubsection{C-2HTR3T-ON}
C-2HTR3T-ON has dedicated recuperators and turbines for the LFR and CSP, allowing for independent inlet temperatures. Three studies were conducted on this cycle with two being constrained and one unconstrained sCO$_2$ LFR inlet conditions. The constrained studies have cold TES temperatures of 390$^{\circ}$C and 440$^{\circ}$, both of which have negligible efficiency differences. Similarly to the studies done on C-1HTR1T-ON, the cold TES temperature had an effect on mass flow rate of solar salt with the 440$^{\circ}$C case having a larger value and therefore higher component cost. The 390$^{\circ}$C unconstrained study has the highest efficiency with a value of 46.10\%, a 1.76\% increase over the constrained cases. Additionally, the sCO$_2$ LFR inlet temperature increased by a value of 15.2$^{\circ}$C to 415.2$^{\circ}$C, having a negative effect on LFR efficiency and heat exchanger parameters.

\hl{again how do I justify the heat exchanger and LFR efficiency gains? I do not have any sources other than what westinghouse has supplied over email and in general meetings}

@@

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

>>>>

The calculated values reported in Table \ref{tab-noncharg} are component power, mass flow fractions, and counter-flow heat exchanger specifications. Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to 400$^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off of a parametric study on the MC mass flow fraction. Values listed in the Cold TES Temperature row are set to values of 390$^{\circ}$C, 410$^{\circ}$C, or 440$^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency and to accommodate certain characteristics of cycle configurations. Cycles with data entries labeled not applicable (N/A) do not contain the component listed and therefore do not have values associated with the component.

@@

The two-cycle configuration has the CSP and LFR operating in separate recompression cycles when the focus is on electrical generation, therefore these two cycles are analyzed individually. C-LFR-ON has the highest efficiency during unconstrained operation with a gain of 1.8\%. The unconstrained case allows for smaller temperature gradient across the LFR, an increase in recuperator effectiveness, and an increase in recuperator capacitance ratio, all of which reduce sources of irreversibility in the cycle \cite{klein_nellis_2011}. According to studies carried out by our industry partner, Westinghouse, increasing the LFR sCO$_2$ inlet temperature above the design value of 400$^{\circ}$C has a negative effect on LFR HX outlet temperature, effectively demanding an ideal LFR heat exchanger. Additionally, Westinghouse concluded that a lower sCO$_2$ LFR inlet temperature, down to 340$^{\circ}$C, is desirable for LFR heat generation efficiency. The sCO$_2$ inlet temperature to the LFR increases by 15.1$^{\circ}$C to a value of 415.1$^{\circ}$C, reducing LFR heat generation efficiency and demanding a larger, more idealized, LFR heat exchanger.   
\hl{would I need more information on the LFR from westinghouse (ie report) to make these statements? additionally a conclusion to these statements needs more supporting detail, should I go with the higher efficiency or the cycle that I know works with design values?}

C-CSP-ON is not affected by constrained or unconstrained LFR sCO$_2$ inlet temperature because the two cycles are not tethered during non-charging configuration. Two individual studies were conducted on the C-CSP-ON cycle cold TES temperature, one with a lower design value of 390$^{\circ}$C and another with a higher value of 440$^{\circ}$C. A cold TES temperature of 410$^{\circ}$C was excluded since it can be presumed to have an efficiency intermediate to the 390$^{\circ}$C and 440$^{\circ}$C calculated values. Cold TES temperature was found to have a negligible effect on cycle efficiency between the two studied cases, with the 440$^{\circ}$C case gaining 0.35\%. The component that has the largest change in values is the CSP HX with a large drop in capacitance ratio and UA value, therefore the lower temperature of 390$^{\circ}$C for cold TES temperature is ideal increasing the performances of the heat exchanger.

\subsubsection{C-1HTR1T-ON}
The single cycle configuration, C-1HTR1T-ON, has the CSP and LFR heat additions in parallel causing identical inlet conditions. Due to the 10$^{\circ}$C approach temperature, the identical inlet conditions lead to a lower bound of 410$^{\circ}$C on the cold TES temperature when the sCO$_2$ LFR inlet temperature is constrained to 400$^{\circ}$C. A supplementary 440$^{\circ}$C cold TES study is ran to test the effects that higher temperature storage has on cycle efficiency. Raising the temperature of the cold TES from 410$^{\circ}$C to 440$^{\circ}$C had no effect on cycle efficiency but did raise the solar salt mass flow rate to accommodate for the lower temperature difference across the CSP HX hot side. Increasing the solar salt mass flow rate requires more storage for the same CSP heat input, a reduction in dispatchability, and larger pumps, increasing the cost of the system. Therefore, a lower cold TES temperature is desirable. Without the constraint on the sCO$_2$ LFR inlet temperature, a study is additionally conducted with cold TES temperature set to 390$^{\circ}$C. Of these three sensitivity studies, the cycle that yielded the highest efficiency is the unconstrained, 390$^{\circ}$C cold TES with an efficiency gain of 0.68\% over the constrained cases. The high temperature difference between the hot and cold TES reduces the mass flow rate of solar salt and subsequent cost of system components. The sCO$_2$ LFR inlet temperature for the 390$^{\circ}$C cold TES study is 380$^{\circ}$C, which increases the performance of the LFR heat exchanger as well as allowing for a higher LFR efficiency.

\subsubsection{C-2HTR3T-ON}
C-2HTR3T-ON has dedicated recuperators and turbines for the LFR and CSP, allowing for independent inlet temperatures. Three studies were conducted on this cycle with two being constrained and one unconstrained sCO$_2$ LFR inlet conditions. The constrained studies have cold TES temperatures of 390$^{\circ}$C and 440$^{\circ}$, both of which have negligible efficiency differences. Similarly to the studies done on C-1HTR1T-ON, the 440$^{\circ}$C cold TES temperature case has a larger mass flow rate of solar salt and therefore increases component cost. The 390$^{\circ}$C unconstrained study has the highest efficiency with a value of 46.10\%, 1.76\% more than the constrained cases. Additionally, the sCO$_2$ LFR inlet temperature is 415.2$^{\circ}$C, 15.2$^{\circ}$C more than constrained cases, causing LFR efficiency and heat exchanger parameters to be less than ideal.

\hl{should I include in table 3 important mass flow rates like solar salt mass flow and total mass flow in sCO2?}

@@

% This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
